Thesis outline

### 2017-07-18 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Updated figures in small scale environment chapter

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_NH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_NH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_NH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_NH}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300_group}
    \caption[N/H versus distance to nearest neighbor and group]{Gas-phase 
    nitrogen abundance versus distance to the nearest galaxy (on the left) and 
    nearest group (on the right).  The top panel shows N/H as a function of the 
    sky separation in \hMpc between the target dwarf galaxy and the neighbor, 
    while the bottom panel shows N/H as a function of the closest virial 
    neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
    black and unknown in green.  We have also included the average nitrogen 
    abundance for the galaxies after binning by distance, to discern any finer 
    behavior in the relationships.  Linear fits to the void and wall galaxies 
    are shown in orange and blue, respectively.  There is very little difference 
    in N/H between the two large-scale environments.  Only the neighbor galaxies 
    at separations less than 0.1$r_{vir}$ appear to have some affect on the 
    dwarf galaxies' nitrogen abundance.  There does not appear to be any 
    relationship between the dwarf galaxies' nitrogen abundance and the distance 
    to their nearest group.}
    \label{fig:NH}
\end{figure}

@@

\begin{table}
    \begin{tabular}{lcccc}
        Property & Slope (void) & Slope (wall) & Intercept (void) & Intercept (wall)\\
        \hline
        \hline
        \multicolumn{5}{c}{Nearest galaxy by distance}\\
        \hline
        $u-r$ & $-0.01\pm 0.027$ & $0.02\pm 0.063$ & $1.05\pm 0.024$ & $1.06\pm 0.031$\\
        sSFR & $0.01\pm 0.042$ & $0.0\pm 0.10$ & $-9.28\pm 0.037$ & $-9.33\pm 0.049$\\
        \OH & $5.35\pm 0.17\times 10^{-2}$ & $0.33\pm 0.08\times 10^{-2}$ & $7.75\pm 0.0011$ & $7.86\pm 0.0007$\\
        \NH & $1.64\pm 0.11\times 10^{-2}$ & $0.62\pm 0.06\times 10^{-2}$ & $6.53\pm 0.0007$ & $6.52\pm 0.0006$\\
        \NO & $-3.70\pm 0.13\times 10^{-2}$ & $0.29\pm 0.07\times 10^{-2}$ & $-1.23\pm 0.0009$ & $-1.35\pm 0.0006$\\
        \hline
        \multicolumn{5}{c}{Nearest galaxy by fraction of virial radius}\\
        \hline
        $u-r$ & $-0.001\pm 0.0043$ & $-0.004\pm 0.0099$ & $1.05\pm 0.026$ & $1.08\pm 0.031$\\
        sSFR & $0.000\pm 0.0066$ & $0.00\pm 0.016$ & $-9.28\pm 0.040$ & $-9.34\pm 0.049$\\
        \OH & $1.41\pm 0.005\times 10^{-2}$ & $0.12\pm 0.08\times 10^{-2}$ & $7.74\pm 0.0002$ & $7.86\pm 0.0001$\\
        \NH & $1.82\pm 0.11\times 10^{-3}$ & $-1.14\pm 0.002\times 10^{-3}$ & $6.53\pm 0.0001$ & $6.52\pm 0.0001$\\
        \NO & $-1.22\pm 0.004\times 10^{-2}$ & $-0.41\pm 0.02\times 10^{-3}$ & $-1.21\pm 0.0002$ & $-1.33\pm 0.0001$\\
        \hline
        \multicolumn{5}{c}{Nearest group by distance}\\
        \hline
        $u-r$ & $0.002\pm 0.0042$ & $-0.002\pm 0.0041$ & $1.03\pm 0.029$ & $1.08\pm 0.033$\\
        sSFR & $-0.003\pm 0.0064$ & $0.006\pm 0.0065$ & $-9.26\pm 0.045$ & $-9.36\pm 0.053$\\
        \OH & $3.65\pm 0.16\times 10^{-4}$ & $2.06\pm 0.19\times 10^{-4}$ & $7.77\pm 0.0001$ & $7.86\pm 0.0001$\\
        \NH & $4.84\pm 0.01\times 10^{-3}$ & $6.30\pm 0.01\times 10^{-3}$ & $6.51\pm 0.00008$ & $6.49\pm 0.0001$\\
        \NO & $4.47\pm 0.01\times 10^{-3}$ & $6.09\pm 0.01\times 10^{-3}$ & $-1.26\pm 0.0001$ & $-1.38\pm 0.0001$\\
        \hline
        \multicolumn{5}{c}{Nearest group by fraction of group radius}\\
        \hline
        $u-r$ & $0.001\pm 0.0015$ & $-0.001\pm 0.0015$ & $1.03\pm 0.031$ & $1.08\pm 0.036$\\
        sSFR & $-0.002\pm 0.0023$ & $0.002\pm 0.0024$ & $-9.24\pm 0.048$ & $-9.37\pm 0.057$\\
        \OH & $8.81\pm 0.02\times 10^{-4}$ & $-8.74\pm 0.19\times 10^{-4}$ & $7.76\pm 0.00005$ & $7.88\pm 0.00005$\\
        \NH & $2.31\pm 0.001\times 10^{-3}$ & $2.47\pm 0.001\times 10^{-3}$ & $6.49\pm 0.00003$ & $6.47\pm 0.00004$\\
        \NO & $1.43\pm 0.002\times 10^{-3}$ & $3.35\pm 0.002\times 10^{-3}$ & $-1.26\pm 0.00005$ & $-1.40\pm 0.00005$
    \end{tabular}
    \caption[Fit parameters of properties versus distances]{Linear fit 
    parameters to various properties of the target dwarf galaxies by their 
    distances to the nearest galaxy in units of \hMpc, the nearest galaxy in 
    units of the neighbor's virial radius, the center of the nearest group in 
    units of \hMpc, and the nearest group in units of the group's rms radius; 
    all objects must be within 300 km/s of the target galaxy.  The slopes are 
    all negligible, quantifying the observations made that the proximity to a 
    galaxy or group has little influence on a dwarf galaxy's evolution.}
    \label{tab:fits}
\end{table}

@@

% Peculiar velocity
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_150}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_600}
    \caption[Sensitivity to peculiar velocity maximum]{Color versus distance to 
    nearest galaxy (in units of \hMpc on top and virial radii on bottom), with a 
    maximum allowed peculiar velocity of 150 km/s in the left panel and 600 km/s 
    in the right panel.  Void galaxies are shown in red, wall in black, and 
    unknown in green.  The galaxies are binned by distance to tease out any 
    trends at smaller distance scales; linear fits to the void and wall galaxies 
    are shown in orange and blue, respectively.  When compared with the two 
    plots in the left panel of Fig. \ref{fig:ur}, we see that there is no 
    significant influence on our results from the choice of maximum peculiar 
    velocity allowed.}
    \label{fig:ur_vpeculiar}
\end{figure}

@@

% Spectroscopic sample v. complete sample
\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
    \caption[Color versus distance of full SDSS dwarf population]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the entire dwarf galaxy population in SDSS DR7.  When 
    compared to the left-hand panel of Fig. \ref{fig:ur}, we see that there is 
    no difference in the results of the analysis by studying only star-forming 
    galaxies with sufficient detection of the various emission lines necessary 
    to estimate the gas-phase chemical abundances.}
    \label{fig:ur_allDwarf}
\end{figure}

We also test the sensitivity of our results to the population of galaxies being 
studied.  Because we want to look at the relationship between distance and the 
gas-phase chemical abundances of the dwarf galaxies, our sample is limited to 
star-forming dwarf galaxies with detected emission lines necessary for 
estimation of the chemical abundances with the Direct $T_e$ method 
\citep[see][for more details]{Douglass17a}.  We perform the same distance 
analysis on all dwarf galaxies detected in SDSS DR7 with respect to their 
color, to understand how our results depend on our sample.  When we compare Fig. 
\ref{fig:ur_allDwarf} with the left-hand panel of Fig. \ref{fig:ur}, we see that 
there is no difference in the correlation between color and distance to the 
nearest neighbor.  It is clear that our selection bias to star-forming dwarf 
galaxies does not influence any trends we observe in our analysis.

% Absolute magnitude distribution of nearest neighbors
\begin{figure}
    \includegraphics[width=\textwidth]{Images/smallScaleEnvironment/Mr_distribution}
    \caption[Distribution of absolute magnitudes of nearest neighbors]{The 
    distributions in absolute magnitude (left panel) and absolute magnitude 
    relative to the target galaxy (right panel) of the nearest neighbor 
    galaxies.  The top row includes those nearest neighbors in units of \hMpc, 
    and the bottom row consists of the nearest neighbors in units of the 
    neighbor's virial radius.  Comparing the two plots in the right panel, we 
    see that the closest galaxy to the target dwarf galaxies is often of equal 
    or fainter magnitude than the target galaxy.  Alternatively, using the 
    virial radius of the neighbor galaxy as a measure of distance often finds a 
    brighter galaxy than the target galaxy, as the bottom right plot shows.}
    \label{fig:Mr_dist}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
    \caption[Color versus distance calculated with redshift]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top and virial radii on 
    the bottom) for the star-forming dwarf galaxies.  The redshift is included 
    when calculating the distance to the nearest neighbor.  While there is still 
    no correlation between distance and color, we do note that there is a gap in 
    the distribution of galaxies around a distance of 0.05 \hMpc or 0.1$r_{vir}$ 
    from the nearest neighbor.}
    \label{fig:ur_xyz}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_NH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_NH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_NH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_NH}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_NH_300_group}
    \caption[N/H versus distance to nearest neighbor and group]{Gas-phase 
    nitrogen abundance versus distance to the nearest galaxy (on the left) and 
    nearest group (on the right).  The top panel shows N/H as a function of the 
    sky separation in \hMpc between the target dwarf galaxy and the neighbor, 
    while the bottom panel shows N/H as a function of the closest virial 
    neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
    black and unknown in green.  We have also included the average nitrogen 
    abundance for the galaxies after binning by distance, to discern any finer 
    behavior in the relationships.  Linear fits to the void and wall galaxies 
    are shown in orange and blue, respectively.  There is very little difference 
    in N/H between the two large-scale environments.  There does not appear to 
    be any relationship between the dwarf galaxies' nitrogen abundance and the 
    distance to their nearest neighbor or group.}
    \label{fig:NH}
\end{figure}

@@

\begin{table}
    \begin{tabular}{lcccc}
        Property & Slope (void) & Slope (wall) & Intercept (void) & Intercept (wall)\\
        \hline
        \hline
        \multicolumn{5}{c}{Nearest galaxy by distance}\\
        \hline
        $u-r$ & $-0.02\pm 0.027$ & $0.02\pm 0.063$ & $1.05\pm 0.024$  & $1.06\pm 0.031$\\
        sSFR  & $0.01\pm 0.042$  & $0.0\pm 0.10$   & $-9.28\pm 0.037$ & $-9.33\pm 0.049$\\
        \OH   & $0.01\pm 0.027$  & $0.06\pm 0.062$ & $7.988\pm 0.024$ & $7.94\pm 0.030$\\
        \NH   & $0.02\pm 0.028$  & $0.10\pm 0.059$ & $6.54\pm 0.026$  & $6.55\pm 0.029$\\
        \NO   & $0.00\pm 0.028$  & $0.04\pm 0.062$ & $-1.45\pm 0.026$ & $-1.39\pm 0.030$\\
        \hline
        \multicolumn{5}{c}{Nearest galaxy by fraction of virial radius}\\
        \hline
        $u-r$ & $-0.001\pm 0.0043$ & $-0.004\pm 0.0099$ & $1.05\pm 0.026$  & $1.08\pm 0.031$\\
        sSFR  & $0.000\pm 0.0066$  & $0.00\pm 0.016$    & $-9.28\pm 0.040$ & $-9.34\pm 0.049$\\
        \OH   & $0.001\pm 0.0042$  & $0.012\pm 0.0099$  & $7.992\pm 0.025$ & $7.94\pm 0.031$\\
        \NH   & $0.000\pm 0.0045$  & $0.009\pm 0.0094$  & $6.55\pm 0.027$  & $6.56\pm 0.029$\\
        \NO   & $-0.001\pm 0.0045$ & $-0.003\pm 0.0098$ & $-1.44\pm 0.027$ & $-1.37\pm 0.031$\\
        \hline
        \multicolumn{5}{c}{Nearest group by distance}\\
        \hline
        $u-r$ & $0.002\pm 0.0042$  & $-0.002\pm 0.0041$ & $1.03\pm 0.029$  & $1.08\pm 0.033$\\
        sSFR  & $-0.003\pm 0.0064$ & $0.006\pm 0.0065$  & $-9.26\pm 0.045$ & $-9.36\pm 0.053$\\
        \OH   & $0.001\pm 0.0041$  & $0.002\pm 0.0041$  & $7.989\pm 0.029$ & $7.95\pm 0.033$\\
        \NH   & $0.007\pm 0.0043$  & $0.006\pm 0.0038$  & $6.51\pm 0.031$  & $6.55\pm 0.031$\\
        \NO   & $0.006\pm 0.0044$  & $0.005\pm 0.0040$  & $-1.48\pm 0.031$ & $-1.40\pm 0.033$\\
        \hline
        \multicolumn{5}{c}{Nearest group by fraction of group radius}\\
        \hline
        $u-r$ & $0.001\pm 0.0018$  & $-0.001\pm 0.0017$ & $1.02\pm 0.033$  & $1.08\pm 0.036$\\
        sSFR  & $-0.002\pm 0.0027$ & $0.002\pm 0.0028$  & $-9.24\pm 0.051$ & $-9.37\pm 0.058$\\
        \OH   & $0.000\pm 0.0017$  & $0.001\pm 0.0017$  & $7.99\pm 0.033$  & $7.95\pm 0.036$\\
        \NH   & $0.003\pm 0.0018$  & $0.004\pm 0.0016$  & $6.50\pm 0.034$  & $6.53\pm 0.034$\\
        \NO   & $0.003\pm 0.0018$  & $0.002\pm 0.0017$  & $-1.50\pm 0.034$ & $-1.42\pm 0.036$
    \end{tabular}
    \caption[Fit parameters of properties versus distances]{Linear fit 
    parameters to various properties of the target dwarf galaxies by their 
    distances to the nearest galaxy in units of \hMpc, the nearest galaxy in 
    units of the neighbor's virial radius, the center of the nearest group in 
    units of \hMpc, and the nearest group in units of the group's rms radius; 
    all objects must be within 300 km/s of the target galaxy.  The slopes are 
    all negligible, quantifying the observations made that the proximity to a 
    galaxy or group has little influence on a dwarf galaxy's evolution.}
    \label{tab:fits}
\end{table}

@@

% Peculiar velocity
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist150_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist600_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist150_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist600_ur}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_150}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_600}
    \caption[Sensitivity to peculiar velocity maximum]{Color versus distance to 
    nearest galaxy (in units of \hMpc on top and virial radii on bottom), with a 
    maximum allowed peculiar velocity of 150 km/s in the left panel and 600 km/s 
    in the right panel.  Void galaxies are shown in red, wall in black, and 
    unknown in green.  The galaxies are binned by distance to tease out any 
    trends at smaller distance scales; linear fits to the void and wall galaxies 
    are shown in orange and blue, respectively.  When compared with the two 
    plots in the left panel of Fig. \ref{fig:ur}, we see that there is no 
    significant influence on our results from the choice of maximum peculiar 
    velocity allowed.}
    \label{fig:ur_vpeculiar}
\end{figure}

@@

% Spectroscopic sample v. complete sample
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_absDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_groupAbsDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_virDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_groupRDist_ur}
%    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/ALLdwarf_ur_300}
    \caption[Color versus distance of full SDSS dwarf population]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on top left and virial 
    radius on the bottom left) and to the center of the nearest group (in units 
    of \hMpc on the top right and group radius on the bottom right) for the 
    entire dwarf galaxy population in SDSS DR7.  When compared to Fig. 
    \ref{fig:ur}, we see that there are some differences in the results of the 
    analysis by studying only star-forming galaxies with sufficient detection of 
    the various emission lines necessary to estimate the gas-phase chemical 
    abundances.  The addition of redder dwarf galaxies to the sample produces an 
    overall inverse relationship between a wall dwarf galaxy's color and the 
    distance to the nearest neighbor in \hMpc.}
    \label{fig:ur_allDwarf}
\end{figure}

We also test the sensitivity of our results to the population of galaxies being 
studied.  Because we want to look at the relationship between distance and the 
gas-phase chemical abundances of the dwarf galaxies, our sample is limited to 
star-forming dwarf galaxies with detected emission lines necessary for 
estimation of the chemical abundances with the Direct $T_e$ method 
\citep[see][for more details]{Douglass17a}.  We perform the same distance 
analysis on all dwarf galaxies detected in SDSS DR7 with respect to their 
color, to understand how our results depend on our sample.  When we compare Fig. 
\ref{fig:ur_allDwarf} with Fig. \ref{fig:ur}, we see that there are some 
differences in the correlation between color and distance to the nearest 
neighbor.  Let us first look at the linear fits to the data.  The upper left 
panel of Fig. \ref{fig:ur_allDwarf} shows that wall dwarf galaxies become redder 
with decreasing distance to their nearest neighbors, while the upper left panel 
of Fig. \ref{fig:ur} shows no such global trend.  In addition, the full dwarf 
galaxy sample also exhibits different behaviors between the void dwarf galaxies 
and the wall dwarf galaxies.  While there is very little relationship between a 
void dwarf galaxy's color and its distance to a nearest neighbor (as seen in 
Fig. \ref{fig:ur}), wall dwarf galaxies are significantly redder than void dwarf 
galaxies within distances of 0.2 \hMpc.  The wall dwarf galaxies in Fig. 
\ref{fig:ur_allDwarf} also show a shift towards bluer colors within 0.05 \hMpc 
of the nearest neighbor.

A similar pattern in seen when the distance to the nearest neighbor is measured 
by $r_{vir}$.  Within $r_{vir}$, the bottom left panel of Fig. 
\ref{fig:ur_allDwarf} shows that wall dwarf galaxies are redder than void dwarf 
galaxies.  Within 0.1$r_{vir}$, wall dwarf galaxies are bluer than the global 
trend.  Similar trends are seen in the relationship between color and distance 
to the nearest group, seen in the right panel of Fig. \ref{fig:ur_allDwarf}.  It 
is clear that our selection bias to star-forming dwarf galaxies influences the 
trends we observe in our analysis.

% Absolute magnitude distribution of nearest neighbors
\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_rabsmag_abs_hist}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_Drabsmag_abs_hist}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_rabsmag_vir_hist}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_Drabsmag_vir_hist}
%    \includegraphics[width=\textwidth]{Images/smallScaleEnvironment/Mr_distribution}
    \caption[Distribution of absolute magnitudes of nearest neighbors]{The 
    distributions in absolute magnitude (left panel) and absolute magnitude 
    relative to the target galaxy (right panel) of the nearest neighbor 
    galaxies.  The top row includes those nearest neighbors in units of \hMpc, 
    and the bottom row consists of the nearest neighbors in units of the 
    neighbor's virial radius.  Comparing the two plots in the right panel, we 
    see that the closest galaxy to the target dwarf galaxies is often of equal 
    or fainter magnitude than the target galaxy.  Alternatively, using the 
    virial radius of the neighbor galaxy as a measure of distance often finds a 
    brighter galaxy than the target galaxy, as the bottom right plot shows.}
    \label{fig:Mr_dist}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_zAbsDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_zVirDist_ur}
%    \includegraphics[width=0.5\textwidth]{Images/smallScaleEnvironment/dwarf_ur_xyz}
    \caption[Color versus distance calculated with redshift]{Color versus 
    distance to the nearest galaxy (in units of \hMpc on the left and virial 
    radius on the right) for the star-forming dwarf galaxies.  The redshift is 
    included when calculating the distance to the nearest neighbor.  While there 
    is still no correlation between distance and color, we do note that there is 
    a gap in the distribution of galaxies around a distance of 0.05 \hMpc or 
    0.2$r_{vir}$ from the nearest neighbor.}
    \label{fig:ur_xyz}
\end{figure}
